\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-23 OaklandSubmission/intro.tex
intro

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of Arithmetic and Boolean compute. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean computations. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks \cite{shafindss,wu,minionn,valeriaMatrix} computing linear classifier, decision trees, deep neural networks, and matrix factorization. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \divya{Moreover, unlike previous systems, our system can scale to arbitrarily large computations using {\em pipelining} (see below). What do we say about Yao pipelining?}
Hence, we show that our framework achieves all three properties of generality, performance and programmer productivity.

\divya{Points.. 1. Prior to our work, there was CBMGC no perf; ABY no prog; 
3. Programmability allows writing programs generating large circuits... 
}

>>>>

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of Arithmetic and Boolean compute. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean computations. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks \cite{shafindss,wu,minionn,valeriaMatrix} computing linear classifier, decision trees, deep neural networks, and matrix factorization. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \divya{Moreover, unlike previous systems, our system can scale to arbitrarily large computations using {\em pipelining} (see below). What do we say about Yao pipelining?}
Hence, we show that our framework achieves all four properties of generality, performance, programmer productivity and scalability.

Prior to our work, there have been systems that provide only a subset of the above properties and lack in remaining properties. For instance, using the framework of CBMC-GC \cite{cbmcgc}, one can write functionalities in high-level language like C but it gives poor performance due to its usage of boolean circuits as underlying representation. Similarly, ABY framework can potentially give good performance but is not programmable. Technique of pipelining Yao garbled circuits \cite{yao-pipe} allowed scaling to lage circuits but gives poor performance. \divya{what about programming?} To summarize, none of the prior frameworks could be used to evaluate the benchmarks such as linear regression, deep neural network prediction etc. In fact, it was widely believed that generic 2PC would not scale to the secure prediction and hence, various protocols were hand-crafted for this task \cite{shafindss,wu,secureml,minionn}. Our framework contradicts this belief.

In this work, we solve an interesting design problem to give a user friendly language that is expressive enough together with a compiler generating efficient secure 2PC protocols.
Programmability and performance of our system has enabled us to write large programs whose circuits  exhaust the memory of the system (~32 GB). To combat this issue, we give a technique called pipelining (see below) that allows scaling of our  scaling of our framework to arbitrary size computations.
